---
title: "Stephen Decker's CV"
author: Stephen Decker
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    css: ['dd_cv.css', 'resume']
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.
# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- TRUE
# Just the copied URL from the sheet
positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/1MY5JRFv3pKLZCtqM3EmfsobBgSVt6v3PhFtv0U-JKQU/edit#gid=1730172225"
# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
sheet_is_publicly_readable <- TRUE
# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE
# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()
# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs
# Functions for building sections from CSV data
source('parsing_functions.R') 
# Load data for CV/Resume
source('gather_data.R')
# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 
```

# Aside

## Connect with Me {#contact}

-   <i class="fa fa-envelope"></i>
    [decker.stephen.t\@gmail.com](mailto:decker.stephen.t@gmail.com){.email}
-   <i class="fa fa-phone"></i> (713) 452-9516
-   <i class="fa fa-twitter"></i>
    \@[decker_st](https://twitter.com/decker_st)

## Links & Resources {#about}

-   <i class="fa fa-file"></i>
    [PubMed](https://pubmed.ncbi.nlm.nih.gov/?sort=date&term=Decker+ST&cauthor_id=30471329)
-   <i class="fa fa-linkedin"></i>
    [LinkedIn](https://www.linkedin.com/in/deckerst/)
-   <i class="fab fa-researchgate"></i>
    [ResearchGate](https://www.researchgate.net/profile/Stephen-Decker-3)
-   <i class="fa fa-github"></i> [Github](https://github.com/stdecker)
-   <i class="fa fa-medium"></i> [Medium](https://medium.com/@decker_st)

## Selected Skills {#skills}

```{r}
build_skill_bars(professional_skills)
```

## Ongoing Projects {#ongoing}

*A Guide for the Analysis of High-Resolution Respirometry Data Using R*.
**Version 2 Available on [GitHub](https://github.com/stdecker)**


## Disclaimer {#disclaimer}

Last updated on `r Sys.Date()` using R version `r getRversion()` and
[**pagedown**](https://github.com/rstudio/pagedown).

# Main

## Stephen Decker{#title}

### PhD, ACSM-CEP 



## Research Experience {data-icon="flask"}

```{r}
research %>% print_section('research_positions')
```




## Education {data-icon="graduation-cap"}

```{r}
research %>% print_section('education')
```



## Selected Publications {data-icon="book-open"}



### Effects of Cigarette Smoke on *In Situ* Mitochondrial Substrate Oxidation of Slow- and Fast-Twitch Skeletal Muscles

**Decker, ST**, Matias, AA, Bannon, ST, Madden, JP, Alexandrou-Majaj, N, Layec, G

N/A

2023

*Life Sciences*

### The Receptor for Advanced Glycation End Products (RAGE) is involved in Mitochondrial Function and Cigarette Smoke-Induced Oxidative Stress [PubMed](https://pubmed.ncbi.nlm.nih.gov/36586455/)

Kwon, OS, **Decker, ST**,  Zhao, J, Hoidal, JR, Hueckstadt, T, Sanders,
KA, Richardson, RS, Layec, G

N/A

2022

*Free Radical Biology & Medicine*


### Skeletal muscle Mitochondrial Adaptations Induced by Long-term Cigarette Smoke Exposure [PubMed](https://www.ncbi.nlm.nih.gov/labs/pmc/articles/PMC8321829/)

**Decker, ST**, Kwon, OS, Zhao, J, Hoidal, JR, Hueckstadt, T, Sanders,
KA, Richardson, RS, Layec, G

N/A

2021

*American Journal of Physiology - Endocrinology & Metabolism*



